manuscript

### 2022-09-15 ms/manuscript.Rmd
try knitting to word

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
bibliography: refs.bib
---

>>>>

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:   
  word_document:
    reference_docx: rv_ms_081921.docx
  pdf_document: default
bibliography: refs.bib
---
